Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$

### 2015-01-22 doc/HH4b_Documentation.tex

The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples. At the generator level the following basic cuts are applied. Each final state particle must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$. Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$. Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.

@@

\subsubsection{Resolved $b$-jet tagging efficiencies}
In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$. In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_l\epsilon^2_b$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.

>>>>

The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples. At the generator level the following basic cuts are applied. Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$. Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$. Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.

@@

\subsubsection{Resolved $b$-jet tagging efficiencies}
In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$. In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_b\epsilon^2_l$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.
